Fast Construction of Inter-Object Spacing Representations

### 2017-04-03 paper.tex
updated figure 5.

  \caption{
    \protect\subref{fig:simple-conflicts} \red{On the bottom right, the box in the 3rd quadrant is not a conflict, and shouldn't be colored red.} A toy dataset showing conflict cells after building the quadtree from object vertices.
    \protect\subref{fig:simple-samples} The toy dataset showing how samples are collected.
  }
  \label{fig:results-toy}
\end{figure}

>>>>

  \caption{
    \protect\subref{fig:simple-conflicts} A toy dataset showing conflict cells after building the quadtree from object vertices.
    \protect\subref{fig:simple-samples} The toy dataset showing how samples are collected.
  }
  \label{fig:results-toy}
\end{figure}
